### 2020-03-23 README.Rmd
run_cv working and example for SCBI and BW

@@

Here I cheated `run_cv` to run the cross valididation for just two training set. It runs on the whole data set up just for `test = fold 23` and `test = fold 2`. Just to see how long it takes.
```{r}
tic()

scbi_cv_predict <- focal_vs_comp_scbi %>%
  run_cv(model_specs = scbi_specs, max_dist = max_dist, cv_grid = scbi_cv_grid)
toc()
```

Running just two folds took 5440 seconds. There are 28 folds. So running everything should take 5440 * 14 / 60 / 60 = 21 hours.

Comapre results

@@

>>>>

**SCBI**

@@

This will fit the model for each fold. On each fold it fits the data for all trees outside of that fold. If you have N folds then `run_cv` will take N-times longer than `fit_bayesain_model`. Here I cheated `run_cv` to fit for just `test = fold 23` and `test = fold 2`. It still fits to all other folds for those two, but only does it twice (rather than 28 times for the SCBI data set). Do this with the arguement `all_folds = FALSE`.

```{r}
tic()
scbi_cv_predict <- focal_vs_comp_scbi %>%
  run_cv(model_specs = scbi_specs, max_dist = max_dist, cv_grid = scbi_cv_grid, all_folds = FALSE)
toc()
```

Running just two folds took 2119 seconds. There are 28 folds. So running everything should take 2119 * 14 / 60 / 60 = 8 hours.

Then we can compare the results to show that the RMSE for the cross-validated fit is larger than for the none CV fit above.

@@

**Big Woods**

Big woods is faster because it has fewer trees, but also because we are fitting the model for trait groups (6 groups) rather than species for SCBI (40 species). The lambda matrix is much smaller (6 x 6 versus 40 x 40). Means it fits much faster.

```{r}
tic()
bw_cv_predict <- focal_vs_comp_bw %>%
  run_cv(model_specs = bw_specs, max_dist = max_dist, cv_grid = bw_cv_grid)
toc()
```

Big Woods must faster because it is a smaller plot? Mabye also because we are fitting the trait group version (6 spp versus 40 for SCBI).

bw_cv_predict %>%
  inner_join(bw_growth_df, by = 'focal_ID', suffix = c('_cv','')) %>%
  summarise(rmse_cv = sqrt(mean((growth - growth_hat_cv)^2)),
            rmse = sqrt(mean((growth - growth_hat)^2)), n() )
